**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**

### 2016-12-22 submission/Westcott_OptiClust_mSphere_2016.Rmd
Fix formatting

---
title: "**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: msystems.csl
fontsize: 11pt
geometry: margin=1.0in
---

>>>>

---
title: "**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: msphere.csl
fontsize: 11pt
geometry: margin=1.0in
---
